\section{Approach}

Extended Berkeley Packet Filter (eBPF) is a flexible virtual machine in the
Linux kernel programmable during runtime from user space. It allows for simple
programs to be safely executed in the kernel space at various hook points. These
simple programs may be written in a subset of C and then compiled into eBPF
instructions, but similar to assembly, it is entirely possible to write the
programs in eBPF instructions yourself. When loaded into the kernel, they are
tested by the in-kernel verifier. This verifier checks the program against a set
of restrictions including a limitation on the number of (eBPF) instructions and
that there are not loops in the
program\footnote{\url{https://www.kernel.org/doc/html/latest/bpf/verifier.html},
accessed \formatdate{7}{6}{2022}} to
ensure the safety of the kernel. Some of these restrictions however can be
circumvented without diminishing the safety of the kernel.
\todo{Rewrite part about loops.}

% How is eBPF used? What can be achieved?
Traditional usage of Berkeley Packet Filter was limited to network applications,
hooking into the traffic control (TC) stage of the linux kernel network stack,
the eXpress Data Path (XDP) or others(?) to allow inspection and filtering of
packets early on in the pipeline. eBPF also allows to hook into other(?)
syscalls widening the range of applications to.. .
\todo{to what? Rewrite. Cite "Complex Complex Network Services with eBPF:
Experiences and Lessons Learned" Miano}

This thesis explores the possibilities in speeding up and enhancing near real
time behavior by using and abusing(?) eBPF on the edge of an IIoT network to select
tasks based on a priority model and the load of the edge device.
